Democracy, Public Support, and Measurement Uncertainty

### 2021-05-12 paper/dcpo_demsupport.Rmd
visualized results for AJPS; coefficent order issue, #27

```{r visualizeAJPS, fig.cap= "\\label{fig:visualizeAJPS}The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=5}

load(here::here("output", "estimates_clsMeanAJPS.RDS"))
load(here::here("output", "estimates_clsAJPS.RDS"))
load(here::here("output", "estimates_dcpoAJPS.RDS"))

result_pooled <- bind_rows(
  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertain$pooled[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertain$pooled[[1]], model = "DCPO")
)

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Support\n (t-1)",
      "Log GDP\n per capita\n (t-1)",
      "GDP per\n capita growth\n (t-1)",
      "Regional\n democracy\n (t-1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n dependence\n (t-1)"),
    time = 3))

@@

df_tableAJPS <- df_plotS %>% mutate(
  conf = paste0("[", round(conf.low, digits = 2), ", ", round(conf.high, digits = 2), "]"),
  group = "Pooled"
) %>% 
  select(term, estimate, conf, n, model, group) %>% 
  fill(n, .direction = "up")

plot_AJPS1 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms))) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  scale_color_grey(start = 0.4, end = 0.8) +
  labs(
    title = "DV: V-Dem Liberal Democracy Index",
    subtitle = "Pooled"
  ) +
  theme(legend.position = "none")

@@

df_plot <- df_result_cls[[2]] %>% 
  mutate(model = "Claassen 2020a")

df_plot <- df_result_clsUncertain[[2]] %>% 
  mutate(model = "Claassen w/ Uncertainty") %>%  
  bind_rows(df_plot)

df_plot <- df_result_dcpoAJPS[[2]] %>% 
  mutate(model = "DCPO") %>%  
  bind_rows(df_plot)

df_plotS <- df_plot %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Support\n demo only\n (t-1)",
      "Support\n auto only\n (t-1)",
      "Log GDP\n per capita\n (t-1)",
      "GDP per\n capita growth\n (t-1)",
      "Regional\n democracy\n (t-1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n dependence\n (t-1)"),
    time = 3)
  )

@@

df_tableAJPS <- df_plotS %>% mutate(
  conf = paste0("[", round(conf.low, digits = 2), ", ", round(conf.high, digits = 2), "]"),
  group = "Regime Spec."
) %>% 
  select(term, estimate, conf, n, model, group) %>% 
  fill(n, .direction = "up") %>% 
  bind_rows(df_tableAJPS) %>% 
  mutate(estimate = round(estimate, digits = 3))

plot_AJPS2 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
    scale_y_discrete(labels = parse(text = levels(terms2))) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  theme(legend.position = "bottom", 
        legend.title = element_blank())

@@

grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol=2, nrow = 2, 
             layout_matrix = rbind(c(1,2), c(3,3)),
             widths = c(2.7, 2.7), heights = c(2.5, 0.2))

@@

```{r num-cls2020a, results='asis', eval = TRUE}
ls_result_cls <-
  map2(tidy_result_cls, glance_result_cls, function(aTidy, aGlance) {
    ls_sum <- list(tidy = aTidy,
                   glance = aGlance)

    class(ls_sum) <- "modelsummary_list"

    return(ls_sum)
  })

names(ls_result_cls) <- c("Pooled OLS 1", "Pooled OLS 2", "GMM 1", "GMM 2")

names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
  "plm::lag(SupDem_trim, 1)" = "Support[t-1]",
  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
)

modelsummary(ls_result_cls, 
             stars = TRUE,
             coef_map = names_coef, 
             output = "latex") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

>>>>

```{r visualizeAJPS, fig.cap= "\\label{fig:visualizeAJPS}The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=8}

# Very weird phenomenon that the same type of rds files needs different ways to read
# Suggesting using the qs or csv data type in future.
load(here::here("output", "estimates_clsMeanAJPS.RDS"))
result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
load(here::here("output", "estimates_dcpoAJPS.RDS"))

result_pooled <- bind_rows(
  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertain$pooled[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertain$pooled[[1]], model = "DCPO")
) %>% 
  mutate(type = "Pooled")

result_gmm <- bind_rows(
  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertain$gmm[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertain$gmm[[1]], model = "DCPO")
) %>% 
  mutate(type = "GMM")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Support\n (t-1)",
      "Log GDP\n per capita\n (t-1)",
      "GDP per\n capita growth\n (t-1)",
      "Regional\n democracy\n (t-1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n dependence\n (t-1)"),
    time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))

@@

# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
# What I've tried
# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
# 2. redefining the order of model in the dataframe or in dwplot 
# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
# 4. Every post online is to reverse

plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms))) +
  scale_color_grey(start = 0.4, end = 0.8) +
  labs(
    title = "DV: V-Dem Liberal Democracy Index",
    subtitle = "Regime Compacted"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

@@

result_regime <- bind_rows(
  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertain$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertain$`pooled-regime`[[1]], model = "DCPO")
) %>% 
  mutate(type = "Pooled")

result_regimeGmm <- bind_rows(
  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertain$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertain$`gmm-regime`[[1]], model = "DCPO")
) %>% 
  mutate(type = "GMM")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Support\n demo only\n (t-1)",
      "Support\n auto only\n (t-1)",
      "Log GDP\n per capita\n (t-1)",
      "GDP per\n capita growth\n (t-1)",
      "Regional\n democracy\n (t-1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n dependence\n (t-1)"),
    time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))

@@

plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
    scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())

@@

grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)

@@

```{r num-cls2020a, results='asis', eval = TRUE}
tb_result_cls <- map(result_cls, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

names(tb_result_cls) <- c("Pooled", "Pooled-Regime", 
                          "GMM", "GMM-Regime")

names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
  "plm::lag(SupDem_trim, 1)" = "Support[t-1]",
  "plm::lag(SupDem_Democ, 1)" = "Support in Democracy",
  "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
)

modelsummary(tb_result_cls,  
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex", 
             title = "Original") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

```{r num-cls2020aUncertain, results='asis', eval = TRUE}
tb_result_clsUncertain <- map(result_clsUncertain, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

names(tb_result_cls) <- c("Pooled", "Pooled-Regime", 
                          "GMM", "GMM-Regime")

names_coef <- c(
  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
  "plm::lag(theta, 1)" = "Support[t-1]",
  "plm::lag(theta_dem, 1)" = "Support in Democracy",
  "plm::lag(theta_aut, 1)" = "Support in Autocracy",
  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
)

modelsummary(tb_result_clsUncertain, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex", 
             title = "W. Uncertainty") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

```{r num-cls2020aDCPO, results='asis', eval = TRUE}
tb_result_DCPO <- map(result_dcpoUncertain, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

names(tb_result_DCPO) <- c("Pooled", "Pooled-Regime", 
                          "GMM", "GMM-Regime")

names_coef <- c(
  "plm::lag(Vdem_libdem, 1:2)1" = "Democracy[t-1]",
  "plm::lag(Vdem_libdem, 1:2)2"  = "Democracy[t-2]",
  "plm::lag(theta, 1)" = "Support[t-1]",
  "plm::lag(theta_dem, 1)" = "Support in Democracy",
  "plm::lag(theta_aut, 1)" = "Support in Autocracy",
  "plm::lag(lg_imp_mdpgdp, 1)" = "Log~GDP~per~capita[t-1]",
  "plm::lag(mdprgdp_grwth, 1)"  = "GDP~per~capita~growth[t-1]",
  "plm::lag(Region_libdem, 1)" = "Regional~democracy[t-1]",
  "plm::lag(muslism_prop_2010, 1)" = "Percent~Muslim[t-1]",
  "plm::lag(dependence_pc_di, 1)" = "Resource~dependence[t-1]"
)

modelsummary(tb_result_DCPO, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex", 
             title = "W. Uncertainty") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```
